Rasterizing prodution per each region

### 2021-04-23 data_check/farms_data_check.Rmd
fixed missed nova scotia salmon points.. one more farm needs to be added to russia salmon now

library(here)
library(dplyr)
library(sf)
library(raster)
library(mapview)

@@

all_farms <- list.files("data/temp_data/", pattern = "rds$", full.names = TRUE) %>% 
  map_df(., readRDS) %>% 
  rename(iso3c = iso3) %>% 
  mutate(source = "modeled") %>% 
  rbind(data %>% mutate(source = "real"))

@@

by_country_type <- all_farms %>%
  st_drop_geometry() %>%
  group_by(iso3c, type) %>%
  summarise(n())

>>>>

library(here)
library(dplyr)
library(sf)
library(raster)
library(mapview)
library(janitor)

@@

all_farms <- list.files("data/temp_data/temp_marine_final", pattern = "rds$", full.names = TRUE) %>% 
  map_df(., readRDS) %>% 
  rename(iso3c = iso3) %>% 
  mutate(source = "modeled") %>% 
  rbind(data %>% mutate(source = "real"))

sources_spreadsheet <- read_csv("analysis/data/mariculture_mapping_sources.csv") %>%
  clean_names() %>%
    mutate(type = case_when(species == "Salmonids" ~ "salmon",
                          species == "Unfed or algae fed shellfish" ~ "bivalve",
                          species == "Shrimp" ~ "shrimp", 
                          species == "Tuna" ~ "tuna", 
                          species == "General Marine Fish" ~ "marine_fish_general", 
                          species == "Crustaceans" ~ "crustaceans"))

all_farms_sources <- all_farms %>%
  left_join(sources_spreadsheet, by = c("iso3c", "type"))

@@

by_country_type <- all_farms %>%
  st_drop_geometry() %>%
  group_by(iso3c, type) %>%
  summarise(n_obs = n()) %>%
  left_join(sources_spreadsheet, by = c("iso3c", "type")) %>%
  dplyr::select(iso3c, type, n_obs, number_of_total_farms) %>%
  mutate(difference = n_obs - number_of_total_farms)

canada_salmon <- all_farms_sources %>%
  dplyr::filter(iso3c == "CAN", 
                type == "salmon")

mapview(canada_salmon)
```

### 2021-04-23 marine/STEP1_species_groups/STEP1_species_groups.Rmd
fixed missed nova scotia salmon points.. one more farm needs to be added to russia salmon now

>>>>

test <- fao_1 %>%
  dplyr::filter(aq_group == "crustaceans")
sum(test$total_tonnes) # 5094133

test <- fao_1 %>%
  dplyr::filter(aq_group == "marine_fish_general")
sum(test$total_tonnes) # 5094133

test <- fao_1 %>%
  dplyr::filter(aq_group == "tuna")
sum(test$total_tonnes) # 5094133

test <- fao_1 %>%
  dplyr::filter(aq_group == "salmonids")
sum(test$total_tonnes) # 5094133
```

### 2021-04-23 marine/bivalve/bivalve_farms/STEP2_bivalve_farm_locations.Rmd
fixed missed nova scotia salmon points.. one more farm needs to be added to russia salmon now

# South Korea 
We currently know the exact location of 27 bivalve farms in South Korea, however there is much more production that just 27 farms. However, FAO says there are 5245 shell fish leases in South Korea. WE will place an additional 5218 farms.

@@

We currently know the exact location of 25 bivalve farms in Peru, however there is much more production that just 25 farms. However, FAO says there are 52 bivalve farms in Peru. We will place an additional 27 farms (for a total of 52 farms).

@@

  - Allocate 266 farms into the most suitable locations in Croatia (this is done later, along with the rest of the gapfilling.)
 - For now we will flag this so that we can gapfill later.

@@

Source: 
The aquaculture sectors in French Polynesia , n.d. . Department of Marine Resources Pu Fa’Ahotu Moana. http://www.ressources-marines.gov.pf/aquaculteurs/laquaculture-en-polynesie-francaise/les-filieres-de-laquaculture-en-polynesie-francaise/

>>>>

# South Korea 
We currently know the exact location of 27 bivalve farms in South Korea. However, FAO says there are 5245 shell fish leases in South Korea. WE will place an additional 5218 farms.

@@

We currently know the exact location of 25 bivalve farms in Peru. However, FAO says there are 52 bivalve farms in Peru. We will place an additional 27 farms (for a total of 52 farms).

@@

  - Allocate 266 farms into the most suitable locations in Croatia (this is done later, along with the rest of the gapfilling.)

@@

Source: 
The aquaculture sectors in French Polynesia , 2019. Department of Marine Resources Pu Fa’Ahotu Moana. http://www.ressources-marines.gov.pf/aquaculteurs/laquaculture-en-polynesie-francaise/les-filieres-de-laquaculture-en-polynesie-francaise/

### 2021-04-23 marine/bivalve/bivalve_farms/STEP4_rasterize_production.Rmd
fixed missed nova scotia salmon points.. one more farm needs to be added to russia salmon now

CHN:HKG
CHN:MAC
ESP:MAR
ESP:PRT
HKG:CHN
HRV:BIH
HRV:MNE
HRV:SVN
IDN:PNG
IRL:GBR
JPN:RUS
KHM:VNM
MEX:USA
MYS:BRN
MYS:THA
NLD:BEL
NLD:DEU
PRK:RUS
PRT:ESP
SVN:ITA
THA:MMR
THA:MYS
TWN:CHN
USA:CAN
USA:MEX
VNM:KHM

>>>>

# CHN:HKG
# CHN:MAC
# ESP:MAR
# ESP:PRT
# HKG:CHN
# HRV:BIH
# HRV:MNE
# HRV:SVN
# IDN:PNG
# IRL:GBR
# JPN:RUS
# KHM:VNM
# MEX:USA
# MYS:BRN
# MYS:THA
# NLD:BEL
# NLD:DEU
# PRK:RUS
# PRT:ESP
# SVN:ITA
# THA:MMR
# THA:MYS
# TWN:CHN
# USA:CAN
# USA:MEX
# VNM:KHM

### 2021-04-23 marine/shrimp/shrimp_farms/STEP1_fao_shrimp_production.Rmd
fixed missed nova scotia salmon points.. one more farm needs to be added to russia salmon now

>>>>

```{r}
## write out shrimp taxa and production for Juliette
fao_shrimp_taxa_prod <- fao %>%
  filter(species %in% shrimp_list) %>%  
  filter(!is.na(value)) %>%
  arrange(-value, country) %>%
  group_by(country, year) %>%
  summarise(value = sum(value)) %>%
  filter(value>=500) %>% # countries with less do not appear to be stable producers at this point
  filter(year == 2017)

sum(fao_shrimp_taxa_prod$value) # 5095394 - adds ~1000 tonnes

unique(fao_shrimp_taxa_prod$country) # 35 countries 
```

### 2021-04-23 marine/shrimp/shrimp_farms/STEP2_shrimp_farm_locations.Rmd
fixed missed nova scotia salmon points.. one more farm needs to be added to russia salmon now

@@

@@

 = “According to the aquaculture method and the scale of production, aquaculture production units are distributed as follows: 15 production units of tilapia cages, 26 reservoirs for household consumption, 50 small and medium scale units, 1 industrial scale unit; 2 ornamental fish production units, 23 units of fresh water prawns, and 39 marine shrimp farms.”

>>>>

https://edepot.wur.nl/531775

@@

Source: 
Van Der Heijden, P., 2020. Aquaculture in Cuba. Aquaculture Europe 45.

@@

 “According to the aquaculture method and the scale of production, aquaculture production units are distributed as follows: 15 production units of tilapia cages, 26 reservoirs for household consumption, 50 small and medium scale units, 1 industrial scale unit; 2 ornamental fish production units, 23 units of fresh water prawns, and 39 marine shrimp farms.”

### 2021-04-23 marine/tuna/tuna_farms/STEP4_rasterize_production.Rmd
fixed missed nova scotia salmon points.. one more farm needs to be added to russia salmon now

all_farms <- list.files("data/temp_data/", pattern = "rds$", full.names = TRUE) %>% 
  map_df(., readRDS) %>% 
  rename(iso3c = iso3) %>% 
  mutate(source = "modeled") %>% 
  #left_join(tonnage_per_farms)
  rbind(data %>% mutate(source = "real"))

>>>>

all_farms <- list.files("data/temp_data/temp_marine_final", pattern = "rds$", full.names = TRUE) %>% 
  map_df(., readRDS) %>% 
  rename(iso3c = iso3) %>% 
  mutate(source = "modeled") %>% 
  #left_join(tonnage_per_farms)
  rbind(data %>% mutate(source = "real"))
